---
title: "Meteorological data - Environment Canada"
author: "Geography Department - Université Laval"
date: "22/06/2021"
update: "25/05/2022"
output: html_document
---

```{r message=FALSE}
library(filesstrings)
library(dplyr)
```

## Reading Environment Canada weather station data
Uses a list of stations with Environment Canada data from 2017 to 2020 saved locally. The list is found in the Data directory

```{r}
liste_station <- read.csv('/Users/jean-philippegilbert/Documents/Université Laval/Cartographie vulnérabilité vagues de chaleur accamblante - General/Data/Donnees_meteo/Station Inventory EN_modif_2.csv')
```

## Downloading weather data from Environment Canada
Once each of the weather stations are integrated into R, the weather data must be downloaded from Environment Canada's servers. They offer a methodology to do this. It can be found here: https://drive.google.com/drive/folders/1WJCDEU34c60IfOnG4rv5EPZ4IhhW9vZH. It uses the Command line.

```{r eval=FALSE}
for (i in 1:nrow(liste_station))
{
  debut <- 'for annee in `seq 2017 2020`;do for mois in `seq 1`;do wget --content-disposition "https://climat.meteo.gc.ca/climate_data/bulk_data_f.html?format=csv&stationID='
  fin <- paste(liste_station$Station.ID[i],'&Year=${annee}&Month=${mois}&Day=14&timeframe=2&submit=++T%C3%A9l%C3%A9charger+% D%0Ades+donn%C3%A9es" ;done;done', sep = "")
  commande <- paste(debut,fin, sep="")
 
  system(commande)
  
  #fait une pause de 5 secondes pour être certain que les données soit toutes téléchargées
  Sys.sleep(5)
  
  #puis déplace les fichiers du dossier de téléchargement vers le dossier désiré.
  
  fichiers <- list.files("FOLDER_DOWNLOAD", pattern = 'fr_climat', full.names = TRUE)
  for (j in 1:length(fichiers))
  {
    file.move(fichiers[j], 'DESIRED_FILE')     
  }
}
```

## Hot Days
Once the meteorological data for each station is downloaded, it is necessary to determine the dates of the hot days, in order to acquire the appropriate ground temperature imagery. We use a modified version of the INSPQ definition of a heat wave: https://www.inspq.qc.ca/pdf/publications/1079_IndicateursVigieSanteChaleur.pdf. According to the INSPQ, a heat wave must have 3 consecutive days with a temperature above 30 celsius and a minimum above 20 celsius. However, following this definition, we do not have images for the entire territory. Therefore, we use the criterion of 30 celsius.


``` {r eval=FALSE}

donnees_meteo <- list.files(path = 'FILE_CONTAINING_METEOROLOGICAL_DATA', full.names = TRUE)
file <- read.csv(donnees_meteo[1],stringsAsFactors = FALSE) 

fichier_journees_chaudes <- file[1,]
for (i in 1:length(donnees_meteo))
{
  file <- read.csv(donnees_meteo[i], stringsAsFactors = FALSE)
  file <- na_if(file, "")
  file$ID.climatologique <- as.character(file$ID.climatologique)
  
    for (j in 1:nrow(file))
    {
      
      if (file$Mois[j] %in% 4:11 && !is.na(file$Temp.max...C.[j]) && !is.na(file$Temp.min...C.[j]))
      {
        if(as.numeric(sub(",",".",file$Temp.max...C.[j])) >= 30)
        {
          print(file$Nom.de.la.Station[j])
          print(file$Date.Heure[j])
          print(file$Temp.max...C.[j])
          print(i)
          print(j)
          fichier_journees_chaudes <- rbind(fichier_journees_chaudes, file[j,])
        #}
      }
    }
  }
  print(i)
}

fichier_journees_chaudes <- fichier_journees_chaudes[-1,]
write.csv(fichier_journees_chaudes,"FILE_CONTAINING_THE_HOT_DAYS_FOR_EACH_STATION")
```


