---
title: "Image_selection_Landsat"
author: "Geography Department - Université Laval"
date: "25/05/2022"
output: html_document
---

## Choice of Landsat images
Recall that the method of calculating the ground temperature is: An Efficient Framework for Producing Landsat-Based Land Surface Temperature Data Using Google Earth Engine. The details of the method can be found in the scientific article. The code to download the images can be found here: https://code.earthengine.google.com/?accept_repo=users/wangmmcug/landsat_psc_lst

It is important to have a Google Earth Engine account, otherwise it will not be possible to access the images.

```{r eval=FALSE}
library(rgee)
ee_Initialize()
```

```{r eval=FALSE}
extraction_date <- function(df)
{#' extraction_date
#'
#' @param df 
#'extracts the dates from the date column and puts them in their own column
#'
#' @return df with three new fields, Year, month et day
#' @export
#'
#' @examples
  
  df$Year <- as.numeric(substr(df$Date, start = 1, stop = 4))
  df$Month <- as.numeric(substr(df$Date, start = 6, stop = 7))
  df$Day <- as.numeric(substr(df$Date, start = 9, stop = 10))
  return(df)
}
```

#Newfoundland and Labrador
```{r eval=FALSE}
region_TNL <- ee$Geometry$BBox(-59.93, 47.00, -50.46, 51.25) #Coordinates of a polygon covering Newfoundland
image_TNL_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_TNL)
image_TNL_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_TNL)
image_TNL_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_TNL)

image_TNL_2018 <- image_TNL_2018$getInfo()
image_TNL_2018_df <- data.frame(1, c(1:length(image_TNL_2018$features)))
image_TNL_2018_df$Date <- 1
image_TNL_2018_df$Row <- 1
image_TNL_2018_df$Path <- 1

image_TNL_2019 <- image_TNL_2019$getInfo()
image_TNL_2019_df <- data.frame(1, c(1:length(image_TNL_2019$features)))
image_TNL_2019_df$Date <- 1
image_TNL_2019_df$Row <- 1
image_TNL_2019_df$Path <- 1

image_TNL_2020 <- image_TNL_2020$getInfo()
image_TNL_2020_df <- data.frame(1, c(1:length(image_TNL_2020$features)))
image_TNL_2020_df$Date <- 1
image_TNL_2020_df$Row <- 1
image_TNL_2020_df$Path <- 1

for (i in 1:length(image_TNL_2018$features))
{
  image_TNL_2018_df$Date[i] <- image_TNL_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_TNL_2018_df$Row[i] <- image_TNL_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_TNL_2018_df$Path[i] <- image_TNL_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_TNL_2019$features))
{
  image_TNL_2019_df$Date[i] <- image_TNL_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_TNL_2019_df$Row[i] <- image_TNL_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_TNL_2019_df$Path[i] <- image_TNL_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_TNL_2020$features))
{
  image_TNL_2020_df$Date[i] <- image_TNL_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_TNL_2020_df$Row[i] <- image_TNL_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_TNL_2020_df$Path[i] <- image_TNL_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_TNL_2018_df <- extraction_date(image_TNL_2018_df)
image_TNL_2019_df <- extraction_date(image_TNL_2019_df)
image_TNL_2020_df <- extraction_date(image_TNL_2020_df)

image_TNL_2018_df <- image_TNL_2018_df[,c(-1:-2)]
image_TNL_2019_df <- image_TNL_2019_df[,c(-1:-2)]
image_TNL_2020_df <- image_TNL_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_TNL <- do.call('rbind', list(image_TNL_2018_df,image_TNL_2019_df,image_TNL_2020_df))
Image_journee_chaude_TNL <- Image_dispo_TNL[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
TN <- donnee_meteo_2[which(donnee_meteo_2$Province == "NEWFOUNDLAND"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_TNL))
{
 for (j in 1:nrow(TN))
 {
   if(as.character(Image_dispo_TNL$Date[i]) == TN$Date.Heure[j])
   {
     Image_journee_chaude_TNL <- rbind(Image_journee_chaude_TNL, Image_dispo_TNL[i,])
   }
 }
  print(i)
}

Image_journee_chaude_TNL <- Image_journee_chaude_TNL[-1,]

#in csv format
write.csv(Image_journee_chaude_TNL, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Ontario south
```{r eval=FALSE}
region_ont_sud <- ee$Geometry$BBox(-83.90, 41.92, -75.46, 45.81) #Coordinates of a polygon covering Southern Ontario
image_ont_sud_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_ont_sud)
image_ont_sud_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_ont_sud)
image_ont_sud_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_ont_sud)

image_ont_sud_2018 <- image_ont_sud_2018$getInfo()
image_ont_sud_2018_df <- data.frame(1, c(1:length(image_ont_sud_2018$features)))
image_ont_sud_2018_df$Date <- 1
image_ont_sud_2018_df$Row <- 1
image_ont_sud_2018_df$Path <- 1

image_ont_sud_2019 <- image_ont_sud_2019$getInfo()
image_ont_sud_2019_df <- data.frame(1, c(1:length(image_ont_sud_2019$features)))
image_ont_sud_2019_df$Date <- 1
image_ont_sud_2019_df$Row <- 1
image_ont_sud_2019_df$Path <- 1

image_ont_sud_2020 <- image_ont_sud_2020$getInfo()
image_ont_sud_2020_df <- data.frame(1, c(1:length(image_ont_sud_2020$features)))
image_ont_sud_2020_df$Date <- 1
image_ont_sud_2020_df$Row <- 1
image_ont_sud_2020_df$Path <- 1

for (i in 1:length(image_ont_sud_2018$features))
{
  image_ont_sud_2018_df$Date[i] <- image_ont_sud_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_ont_sud_2018_df$Row[i] <- image_ont_sud_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_ont_sud_2018_df$Path[i] <- image_ont_sud_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_ont_sud_2019$features))
{
  image_ont_sud_2019_df$Date[i] <- image_ont_sud_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_ont_sud_2019_df$Row[i] <- image_ont_sud_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_ont_sud_2019_df$Path[i] <- image_ont_sud_2019$features[i][[1]]$properties$TARGET_WRS_PATH# Export Path
}

for (i in 1:length(image_ont_sud_2020$features))
{
  image_ont_sud_2020_df$Date[i] <- image_ont_sud_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_ont_sud_2020_df$Row[i] <- image_ont_sud_2020$features[i][[1]]$properties$TARGET_WRS_ROW  #Export Row
  image_ont_sud_2020_df$Path[i] <- image_ont_sud_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
} 

image_ont_sud_2018_df <- extraction_date(image_ont_sud_2018_df)
image_ont_sud_2019_df <- extraction_date(image_ont_sud_2019_df)
image_ont_sud_2020_df <- extraction_date(image_ont_sud_2020_df)

image_ont_sud_2018_df <- image_ont_sud_2018_df[,c(-1:-2)]
image_ont_sud_2019_df <- image_ont_sud_2019_df[,c(-1:-2)]
image_ont_sud_2020_df <- image_ont_sud_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_ont_sud <- do.call('rbind', list(image_ont_sud_2018_df,image_ont_sud_2019_df,image_ont_sud_2020_df))
Image_journee_chaude_ont_sud <- Image_dispo_ont_sud[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "ONTARIO"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_ont_sud))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_ont_sud$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_ont_sud <- rbind(Image_journee_chaude_ont_sud, Image_dispo_ont_sud[i,])
    }
  }
  print(i)
}

Image_journee_chaude_ont_sud <- Image_journee_chaude_ont_sud[-1,]

#in csv format
write.csv(Image_journee_chaude_ont_sud, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Ontario centre
```{r eval=FALSE}
region_ont_milieu <- ee$Geometry$BBox(-84.90, 46.00, -78.16, 48.9) #Coordinates of a polygon covering the middle of Ontario
image_ont_milieu_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_ont_milieu)
image_ont_milieu_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_ont_milieu)
image_ont_milieu_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_ont_milieu)

image_ont_milieu_2018 <- image_ont_milieu_2018$getInfo()
image_ont_milieu_2018_df <- data.frame(1, c(1:length(image_ont_milieu_2018$features)))
image_ont_milieu_2018_df$Date <- 1
image_ont_milieu_2018_df$Row <- 1
image_ont_milieu_2018_df$Path <- 1

image_ont_milieu_2019 <- image_ont_milieu_2019$getInfo()
image_ont_milieu_2019_df <- data.frame(1, c(1:length(image_ont_milieu_2019$features)))
image_ont_milieu_2019_df$Date <- 1
image_ont_milieu_2019_df$Row <- 1
image_ont_milieu_2019_df$Path <- 1

image_ont_milieu_2020 <- image_ont_milieu_2020$getInfo()
image_ont_milieu_2020_df <- data.frame(1, c(1:length(image_ont_milieu_2020$features)))
image_ont_milieu_2020_df$Date <- 1
image_ont_milieu_2020_df$Row <- 1
image_ont_milieu_2020_df$Path <- 1

for (i in 1:length(image_ont_milieu_2018$features))
{
  image_ont_milieu_2018_df$Date[i] <- image_ont_milieu_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_ont_milieu_2018_df$Row[i] <- image_ont_milieu_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_ont_milieu_2018_df$Path[i] <- image_ont_milieu_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_ont_milieu_2019$features))
{
  image_ont_milieu_2019_df$Date[i] <- image_ont_milieu_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_ont_milieu_2019_df$Row[i] <- image_ont_milieu_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_ont_milieu_2019_df$Path[i] <- image_ont_milieu_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_ont_milieu_2020$features))
{
  image_ont_milieu_2020_df$Date[i] <- image_ont_milieu_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_ont_milieu_2020_df$Row[i] <- image_ont_milieu_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_ont_milieu_2020_df$Path[i] <- image_ont_milieu_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_ont_milieu_2018_df <- extraction_date(image_ont_milieu_2018_df)
image_ont_milieu_2019_df <- extraction_date(image_ont_milieu_2019_df)
image_ont_milieu_2020_df <- extraction_date(image_ont_milieu_2020_df)

image_ont_milieu_2018_df <- image_ont_milieu_2018_df[,c(-1:-2)]
image_ont_milieu_2019_df <- image_ont_milieu_2019_df[,c(-1:-2)]
image_ont_milieu_2020_df <- image_ont_milieu_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_ont_milieu <- do.call('rbind', list(image_ont_milieu_2018_df,image_ont_milieu_2019_df,image_ont_milieu_2020_df))
Image_journee_chaude_ont_milieu <- Image_dispo_ont_milieu[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "ONTARIO"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_ont_milieu))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_ont_milieu$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_ont_milieu <- rbind(Image_journee_chaude_ont_milieu, Image_dispo_ont_milieu[i,])
    }
  }
  print(i)
}

Image_journee_chaude_ont_milieu <- Image_journee_chaude_ont_milieu[-1,]

#in csv format
write.csv(Image_journee_chaude_ont_milieu, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Ontario west
```{r eval=FALSE}
region_ont_ouest <- ee$Geometry$BBox(-95.26, 47.86, -88.29, 49.88) #Coordinates of a polygon covering Western Ontario
image_ont_ouest_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_ont_ouest)
image_ont_ouest_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_ont_ouest)
image_ont_ouest_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_ont_ouest)

image_ont_ouest_2018 <- image_ont_ouest_2018$getInfo()
image_ont_ouest_2018_df <- data.frame(1, c(1:length(image_ont_ouest_2018$features)))
image_ont_ouest_2018_df$Date <- 1
image_ont_ouest_2018_df$Row <- 1
image_ont_ouest_2018_df$Path <- 1

image_ont_ouest_2019 <- image_ont_ouest_2019$getInfo()
image_ont_ouest_2019_df <- data.frame(1, c(1:length(image_ont_ouest_2019$features)))
image_ont_ouest_2019_df$Date <- 1
image_ont_ouest_2019_df$Row <- 1
image_ont_ouest_2019_df$Path <- 1

image_ont_ouest_2020 <- image_ont_ouest_2020$getInfo()
image_ont_ouest_2020_df <- data.frame(1, c(1:length(image_ont_ouest_2020$features)))
image_ont_ouest_2020_df$Date <- 1
image_ont_ouest_2020_df$Row <- 1
image_ont_ouest_2020_df$Path <- 1

for (i in 1:length(image_ont_ouest_2018$features))
{
  image_ont_ouest_2018_df$Date[i] <- image_ont_ouest_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_ont_ouest_2018_df$Row[i] <- image_ont_ouest_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_ont_ouest_2018_df$Path[i] <- image_ont_ouest_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_ont_ouest_2019$features))
{
  image_ont_ouest_2019_df$Date[i] <- image_ont_ouest_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_ont_ouest_2019_df$Row[i] <- image_ont_ouest_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_ont_ouest_2019_df$Path[i] <- image_ont_ouest_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_ont_ouest_2020$features))
{
  image_ont_ouest_2020_df$Date[i] <- image_ont_ouest_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_ont_ouest_2020_df$Row[i] <- image_ont_ouest_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_ont_ouest_2020_df$Path[i] <- image_ont_ouest_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_ont_ouest_2018_df <- extraction_date(image_ont_ouest_2018_df)
image_ont_ouest_2019_df <- extraction_date(image_ont_ouest_2019_df)
image_ont_ouest_2020_df <- extraction_date(image_ont_ouest_2020_df)

image_ont_ouest_2018_df <- image_ont_ouest_2018_df[,c(-1:-2)]
image_ont_ouest_2019_df <- image_ont_ouest_2019_df[,c(-1:-2)]
image_ont_ouest_2020_df <- image_ont_ouest_2020_df[,c(-1:-2)]


#combines files together
Image_dispo_ont_ouest <- do.call('rbind', list(image_ont_ouest_2018_df,image_ont_ouest_2019_df,image_ont_ouest_2020_df))
Image_journee_chaude_ont_ouest <- Image_dispo_ont_ouest[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "ONTARIO"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_ont_ouest))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_ont_ouest$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_ont_ouest <- rbind(Image_journee_chaude_ont_ouest, Image_dispo_ont_ouest[i,])
    }
  }
  print(i)
}

Image_journee_chaude_ont_ouest <- Image_journee_chaude_ont_ouest[-1,]

#in csv format
write.csv(Image_journee_chaude_ont_ouest, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Manitoba south
```{r eval=FALSE}
region_manitoba_sud <- ee$Geometry$BBox(-101.41, 48.99, -96.09, 50.80) #Coordinates of a polygon covering southern Manitoba
image_manitoba_sud_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_manitoba_sud)
image_manitoba_sud_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_manitoba_sud)
image_manitoba_sud_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_manitoba_sud)

image_manitoba_sud_2018 <- image_manitoba_sud_2018$getInfo()
image_manitoba_sud_2018_df <- data.frame(1, c(1:length(image_manitoba_sud_2018$features)))
image_manitoba_sud_2018_df$Date <- 1
image_manitoba_sud_2018_df$Row <- 1
image_manitoba_sud_2018_df$Path <- 1

image_manitoba_sud_2019 <- image_manitoba_sud_2019$getInfo()
image_manitoba_sud_2019_df <- data.frame(1, c(1:length(image_manitoba_sud_2019$features)))
image_manitoba_sud_2019_df$Date <- 1
image_manitoba_sud_2019_df$Row <- 1
image_manitoba_sud_2019_df$Path <- 1

image_manitoba_sud_2020 <- image_manitoba_sud_2020$getInfo()
image_manitoba_sud_2020_df <- data.frame(1, c(1:length(image_manitoba_sud_2020$features)))
image_manitoba_sud_2020_df$Date <- 1
image_manitoba_sud_2020_df$Row <- 1
image_manitoba_sud_2020_df$Path <- 1

for (i in 1:length(image_manitoba_sud_2018$features))
{
  image_manitoba_sud_2018_df$Date[i] <- image_manitoba_sud_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_manitoba_sud_2018_df$Row[i] <- image_manitoba_sud_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_manitoba_sud_2018_df$Path[i] <- image_manitoba_sud_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_manitoba_sud_2019$features))
{
  image_manitoba_sud_2019_df$Date[i] <- image_manitoba_sud_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_manitoba_sud_2019_df$Row[i] <- image_manitoba_sud_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_manitoba_sud_2019_df$Path[i] <- image_manitoba_sud_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_manitoba_sud_2020$features))
{
  image_manitoba_sud_2020_df$Date[i] <- image_manitoba_sud_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_manitoba_sud_2020_df$Row[i] <- image_manitoba_sud_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_manitoba_sud_2020_df$Path[i] <- image_manitoba_sud_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_manitoba_sud_2018_df <- extraction_date(image_manitoba_sud_2018_df)
image_manitoba_sud_2019_df <- extraction_date(image_manitoba_sud_2019_df)
image_manitoba_sud_2020_df <- extraction_date(image_manitoba_sud_2020_df)

image_manitoba_sud_2018_df <- image_manitoba_sud_2018_df[,c(-1:-2)]
image_manitoba_sud_2019_df <- image_manitoba_sud_2019_df[,c(-1:-2)]
image_manitoba_sud_2020_df <- image_manitoba_sud_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_manitoba_sud <- do.call('rbind', list(image_manitoba_sud_2018_df,image_manitoba_sud_2019_df,image_manitoba_sud_2020_df))
Image_journee_chaude_manitoba_sud <- Image_dispo_manitoba_sud[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "MANITOBA"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_manitoba_sud))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_manitoba_sud$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_manitoba_sud <- rbind(Image_journee_chaude_manitoba_sud, Image_dispo_manitoba_sud[i,])
    }
  }
  print(i)
}

Image_journee_chaude_manitoba_sud <- Image_journee_chaude_manitoba_sud[-1,]
write.csv(Image_journee_chaude_manitoba_sud, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Manitoba north
```{r eval=FALSE}
region_manitoba_nord <- ee$Geometry$BBox(-98.01, 55.67, -97.67, 55.86) #Coordinates of a polygon covering northern Manitoba
image_manitoba_nord_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_manitoba_nord)
image_manitoba_nord_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_manitoba_nord)
image_manitoba_nord_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_manitoba_nord)

image_manitoba_nord_2018 <- image_manitoba_nord_2018$getInfo()
image_manitoba_nord_2018_df <- data.frame(1, c(1:length(image_manitoba_nord_2018$features)))
image_manitoba_nord_2018_df$Date <- 1
image_manitoba_nord_2018_df$Row <- 1
image_manitoba_nord_2018_df$Path <- 1

image_manitoba_nord_2019 <- image_manitoba_nord_2019$getInfo()
image_manitoba_nord_2019_df <- data.frame(1, c(1:length(image_manitoba_nord_2019$features)))
image_manitoba_nord_2019_df$Date <- 1
image_manitoba_nord_2019_df$Row <- 1
image_manitoba_nord_2019_df$Path <- 1

image_manitoba_nord_2020 <- image_manitoba_nord_2020$getInfo()
image_manitoba_nord_2020_df <- data.frame(1, c(1:length(image_manitoba_nord_2020$features)))
image_manitoba_nord_2020_df$Date <- 1
image_manitoba_nord_2020_df$Row <- 1
image_manitoba_nord_2020_df$Path <- 1

for (i in 1:length(image_manitoba_nord_2018$features))
{
  image_manitoba_nord_2018_df$Date[i] <- image_manitoba_nord_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_manitoba_nord_2018_df$Row[i] <- image_manitoba_nord_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_manitoba_nord_2018_df$Path[i] <- image_manitoba_nord_2018$features[i][[1]]$properties$TARGET_WRS_PATH  #Export Path
}

for (i in 1:length(image_manitoba_nord_2019$features))
{
  image_manitoba_nord_2019_df$Date[i] <- image_manitoba_nord_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_manitoba_nord_2019_df$Row[i] <- image_manitoba_nord_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_manitoba_nord_2019_df$Path[i] <- image_manitoba_nord_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_manitoba_nord_2020$features))
{
  image_manitoba_nord_2020_df$Date[i] <- image_manitoba_nord_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_manitoba_nord_2020_df$Row[i] <- image_manitoba_nord_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_manitoba_nord_2020_df$Path[i] <- image_manitoba_nord_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_manitoba_nord_2018_df <- extraction_date(image_manitoba_nord_2018_df)
image_manitoba_nord_2019_df <- extraction_date(image_manitoba_nord_2019_df)
image_manitoba_nord_2020_df <- extraction_date(image_manitoba_nord_2020_df)

image_manitoba_nord_2018_df <- image_manitoba_nord_2018_df[,c(-1:-2)]
image_manitoba_nord_2019_df <- image_manitoba_nord_2019_df[,c(-1:-2)]
image_manitoba_nord_2020_df <- image_manitoba_nord_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_manitoba_nord <- do.call('rbind', list(image_manitoba_nord_2018_df,image_manitoba_nord_2019_df,image_manitoba_nord_2020_df))
Image_journee_chaude_manitoba_nord <- Image_dispo_manitoba_nord[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "MANITOBA"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_manitoba_nord))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_manitoba_nord$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_manitoba_nord <- rbind(Image_journee_chaude_manitoba_nord, Image_dispo_manitoba_nord[i,])
    }
  }
  print(i)
}

Image_journee_chaude_manitoba_nord <- Image_journee_chaude_manitoba_nord[-1,]

#in csv format
write.csv(Image_journee_chaude_manitoba_nord, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Saskatchewan
```{r eval=FALSE}
region_sask <- ee$Geometry$BBox(-110.20, 48.94, -101.81, 53.74) #Coordinates of a polygon covering Saskatchewan
image_sask_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_sask)
image_sask_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_sask)
image_sask_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_sask)

image_sask_2018 <- image_sask_2018$getInfo()
image_sask_2018_df <- data.frame(1, c(1:length(image_sask_2018$features)))
image_sask_2018_df$Date <- 1
image_sask_2018_df$Row <- 1
image_sask_2018_df$Path <- 1

image_sask_2019 <- image_sask_2019$getInfo()
image_sask_2019_df <- data.frame(1, c(1:length(image_sask_2019$features)))
image_sask_2019_df$Date <- 1
image_sask_2019_df$Row <- 1
image_sask_2019_df$Path <- 1

image_sask_2020 <- image_sask_2020$getInfo()
image_sask_2020_df <- data.frame(1, c(1:length(image_sask_2020$features)))
image_sask_2020_df$Date <- 1
image_sask_2020_df$Row <- 1
image_sask_2020_df$Path <- 1

for (i in 1:length(image_sask_2018$features))
{
  image_sask_2018_df$Date[i] <- image_sask_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_sask_2018_df$Row[i] <- image_sask_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_sask_2018_df$Path[i] <- image_sask_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_sask_2019$features))
{
  image_sask_2019_df$Date[i] <- image_sask_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_sask_2019_df$Row[i] <- image_sask_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_sask_2019_df$Path[i] <- image_sask_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_sask_2020$features))
{
  image_sask_2020_df$Date[i] <- image_sask_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_sask_2020_df$Row[i] <- image_sask_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_sask_2020_df$Path[i] <- image_sask_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_sask_2018_df <- extraction_date(image_sask_2018_df)
image_sask_2019_df <- extraction_date(image_sask_2019_df)
image_sask_2020_df <- extraction_date(image_sask_2020_df)

image_sask_2018_df <- image_sask_2018_df[,c(-1:-2)]
image_sask_2019_df <- image_sask_2019_df[,c(-1:-2)]
image_sask_2020_df <- image_sask_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_sask <- do.call('rbind', list(image_sask_2018_df,image_sask_2019_df,image_sask_2020_df))
Image_journee_chaude_sask <- Image_dispo_sask[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "SASKATCHEWAN"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_sask))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_sask$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_sask <- rbind(Image_journee_chaude_sask, Image_dispo_sask[i,])
    }
  }
  print(i)
}

Image_journee_chaude_sask <- Image_journee_chaude_sask[-1,]

#in csv format
write.csv(Image_journee_chaude_sask, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```


#Alberta south
```{r eval=FALSE}
region_alberta_sud <- ee$Geometry$BBox(-117.99, 48.98, -109.99, 54.11) #Coordinates of a polygon covering southern Alberta
image_alberta_sud_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_alberta_sud)
image_alberta_sud_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_alberta_sud)
image_alberta_sud_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_alberta_sud)

image_alberta_sud_2018 <- image_alberta_sud_2018$getInfo()
image_alberta_sud_2018_df <- data.frame(1, c(1:length(image_alberta_sud_2018$features)))
image_alberta_sud_2018_df$Date <- 1
image_alberta_sud_2018_df$Row <- 1
image_alberta_sud_2018_df$Path <- 1

image_alberta_sud_2019 <- image_alberta_sud_2019$getInfo()
image_alberta_sud_2019_df <- data.frame(1, c(1:length(image_alberta_sud_2019$features)))
image_alberta_sud_2019_df$Date <- 1
image_alberta_sud_2019_df$Row <- 1
image_alberta_sud_2019_df$Path <- 1

image_alberta_sud_2020 <- image_alberta_sud_2020$getInfo()
image_alberta_sud_2020_df <- data.frame(1, c(1:length(image_alberta_sud_2020$features)))
image_alberta_sud_2020_df$Date <- 1
image_alberta_sud_2020_df$Row <- 1
image_alberta_sud_2020_df$Path <- 1

for (i in 1:length(image_alberta_sud_2018$features))
{
  image_alberta_sud_2018_df$Date[i] <- image_alberta_sud_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_alberta_sud_2018_df$Row[i] <- image_alberta_sud_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_alberta_sud_2018_df$Path[i] <- image_alberta_sud_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_alberta_sud_2019$features))
{
  image_alberta_sud_2019_df$Date[i] <- image_alberta_sud_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_alberta_sud_2019_df$Row[i] <- image_alberta_sud_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_alberta_sud_2019_df$Path[i] <- image_alberta_sud_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_alberta_sud_2020$features))
{
  image_alberta_sud_2020_df$Date[i] <- image_alberta_sud_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_alberta_sud_2020_df$Row[i] <- image_alberta_sud_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_alberta_sud_2020_df$Path[i] <- image_alberta_sud_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_alberta_sud_2018_df <- extraction_date(image_alberta_sud_2018_df)
image_alberta_sud_2019_df <- extraction_date(image_alberta_sud_2019_df)
image_alberta_sud_2020_df <- extraction_date(image_alberta_sud_2020_df)

image_alberta_sud_2018_df <- image_alberta_sud_2018_df[,c(-1:-2)]
image_alberta_sud_2019_df <- image_alberta_sud_2019_df[,c(-1:-2)]
image_alberta_sud_2020_df <- image_alberta_sud_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_alberta_sud <- do.call('rbind', list(image_alberta_sud_2018_df,image_alberta_sud_2019_df,image_alberta_sud_2020_df))
Image_journee_chaude_alberta_sud <- Image_dispo_alberta_sud[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "ALBERTA"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_alberta_sud))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_alberta_sud$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_alberta_sud <- rbind(Image_journee_chaude_alberta_sud, Image_dispo_alberta_sud[i,])
    }
  }
  print(i)
}

Image_journee_chaude_alberta_sud <- Image_journee_chaude_alberta_sud[-1,]

#in csv format
write.csv(Image_journee_chaude_alberta_sud, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Alberta north
```{r eval=FALSE} 
region_alberta_nord <- ee$Geometry$BBox(-114.72, 55.43, -108.94, 60.14) #Coordinates of a polygon covering northern Alberta
image_alberta_nord_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_alberta_nord)
image_alberta_nord_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_alberta_nord)
image_alberta_nord_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_alberta_nord)

image_alberta_nord_2018 <- image_alberta_nord_2018$getInfo()
image_alberta_nord_2018_df <- data.frame(1, c(1:length(image_alberta_nord_2018$features)))
image_alberta_nord_2018_df$Date <- 1
image_alberta_nord_2018_df$Row <- 1
image_alberta_nord_2018_df$Path <- 1

image_alberta_nord_2019 <- image_alberta_nord_2019$getInfo()
image_alberta_nord_2019_df <- data.frame(1, c(1:length(image_alberta_nord_2019$features)))
image_alberta_nord_2019_df$Date <- 1
image_alberta_nord_2019_df$Row <- 1
image_alberta_nord_2019_df$Path <- 1

image_alberta_nord_2020 <- image_alberta_nord_2020$getInfo()
image_alberta_nord_2020_df <- data.frame(1, c(1:length(image_alberta_nord_2020$features)))
image_alberta_nord_2020_df$Date <- 1
image_alberta_nord_2020_df$Row <- 1
image_alberta_nord_2020_df$Path <- 1

for (i in 1:length(image_alberta_nord_2018$features))
{
  image_alberta_nord_2018_df$Date[i] <- image_alberta_nord_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_alberta_nord_2018_df$Row[i] <- image_alberta_nord_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_alberta_nord_2018_df$Path[i] <- image_alberta_nord_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_alberta_nord_2019$features))
{
  image_alberta_nord_2019_df$Date[i] <- image_alberta_nord_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_alberta_nord_2019_df$Row[i] <- image_alberta_nord_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_alberta_nord_2019_df$Path[i] <- image_alberta_nord_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_alberta_nord_2020$features))
{
  image_alberta_nord_2020_df$Date[i] <- image_alberta_nord_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_alberta_nord_2020_df$Row[i] <- image_alberta_nord_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_alberta_nord_2020_df$Path[i] <- image_alberta_nord_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_alberta_nord_2018_df <- extraction_date(image_alberta_nord_2018_df)
image_alberta_nord_2019_df <- extraction_date(image_alberta_nord_2019_df)
image_alberta_nord_2020_df <- extraction_date(image_alberta_nord_2020_df)

image_alberta_nord_2018_df <- image_alberta_nord_2018_df[,c(-1:-2)]
image_alberta_nord_2019_df <- image_alberta_nord_2019_df[,c(-1:-2)]
image_alberta_nord_2020_df <- image_alberta_nord_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_alberta_nord <- do.call('rbind', list(image_alberta_nord_2018_df,image_alberta_nord_2019_df,image_alberta_nord_2020_df))
Image_journee_chaude_alberta_nord <- Image_dispo_alberta_nord[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "ALBERTA"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_alberta_nord))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_alberta_nord$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_alberta_nord <- rbind(Image_journee_chaude_alberta_nord, Image_dispo_alberta_nord[i,])
    }
  }
  print(i)
}

Image_journee_chaude_alberta_nord <- Image_journee_chaude_alberta_nord[-1,]

#in csv format
write.csv(Image_journee_chaude_alberta_nord, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#British Columbia south
```{r eval=FALSE}
region_bc_sud <- ee$Geometry$BBox(-127.28, 48.34, -112.61, 52.57) #Coordinates of a polygon covering southern British Columbia
image_bc_sud_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_bc_sud)
image_bc_sud_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_bc_sud)
image_bc_sud_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_bc_sud)

image_bc_sud_2018 <- image_bc_sud_2018$getInfo()
image_bc_sud_2018_df <- data.frame(1, c(1:length(image_bc_sud_2018$features)))
image_bc_sud_2018_df$Date <- 1
image_bc_sud_2018_df$Row <- 1
image_bc_sud_2018_df$Path <- 1

image_bc_sud_2019 <- image_bc_sud_2019$getInfo()
image_bc_sud_2019_df <- data.frame(1, c(1:length(image_bc_sud_2019$features)))
image_bc_sud_2019_df$Date <- 1
image_bc_sud_2019_df$Row <- 1
image_bc_sud_2019_df$Path <- 1

image_bc_sud_2020 <- image_bc_sud_2020$getInfo()
image_bc_sud_2020_df <- data.frame(1, c(1:length(image_bc_sud_2020$features)))
image_bc_sud_2020_df$Date <- 1
image_bc_sud_2020_df$Row <- 1
image_bc_sud_2020_df$Path <- 1

for (i in 1:length(image_bc_sud_2018$features))
{
  image_bc_sud_2018_df$Date[i] <- image_bc_sud_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_bc_sud_2018_df$Row[i] <- image_bc_sud_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_bc_sud_2018_df$Path[i] <- image_bc_sud_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
} 

for (i in 1:length(image_bc_sud_2019$features))
{
  image_bc_sud_2019_df$Date[i] <- image_bc_sud_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_bc_sud_2019_df$Row[i] <- image_bc_sud_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_bc_sud_2019_df$Path[i] <- image_bc_sud_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_bc_sud_2020$features))
{
  image_bc_sud_2020_df$Date[i] <- image_bc_sud_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_bc_sud_2020_df$Row[i] <- image_bc_sud_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_bc_sud_2020_df$Path[i] <- image_bc_sud_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_bc_sud_2018_df <- extraction_date(image_bc_sud_2018_df)
image_bc_sud_2019_df <- extraction_date(image_bc_sud_2019_df)
image_bc_sud_2020_df <- extraction_date(image_bc_sud_2020_df)

image_bc_sud_2018_df <- image_bc_sud_2018_df[,c(-1:-2)]
image_bc_sud_2019_df <- image_bc_sud_2019_df[,c(-1:-2)]
image_bc_sud_2020_df <- image_bc_sud_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_bc_sud <- do.call('rbind', list(image_bc_sud_2018_df,image_bc_sud_2019_df,image_bc_sud_2020_df))
Image_journee_chaude_bc_sud <- Image_dispo_bc_sud[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "BRITISH COLUMBIA"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_bc_sud))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_bc_sud$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_bc_sud <- rbind(Image_journee_chaude_bc_sud, Image_dispo_bc_sud[i,])
    }
  }
  print(i)
}

Image_journee_chaude_bc_sud <- Image_journee_chaude_bc_sud[-1,]

#in csv format
write.csv(Image_journee_chaude_bc_sud, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#British Columbia North-East
```{r eval=FALSE}
region_bc_ne <- ee$Geometry$BBox(-125.31, 51.27, -119.97, 56.47) #Coordinates of a polygon covering northeastern British Columbia
image_bc_ne_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_bc_ne)
image_bc_ne_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_bc_ne)
image_bc_ne_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_bc_ne)

image_bc_ne_2018 <- image_bc_ne_2018$getInfo()
image_bc_ne_2018_df <- data.frame(1, c(1:length(image_bc_ne_2018$features)))
image_bc_ne_2018_df$Date <- 1
image_bc_ne_2018_df$Row <- 1
image_bc_ne_2018_df$Path <- 1

image_bc_ne_2019 <- image_bc_ne_2019$getInfo()
image_bc_ne_2019_df <- data.frame(1, c(1:length(image_bc_ne_2019$features)))
image_bc_ne_2019_df$Date <- 1
image_bc_ne_2019_df$Row <- 1
image_bc_ne_2019_df$Path <- 1

image_bc_ne_2020 <- image_bc_ne_2020$getInfo()
image_bc_ne_2020_df <- data.frame(1, c(1:length(image_bc_ne_2020$features)))
image_bc_ne_2020_df$Date <- 1
image_bc_ne_2020_df$Row <- 1
image_bc_ne_2020_df$Path <- 1

for (i in 1:length(image_bc_ne_2018$features))
{
  image_bc_ne_2018_df$Date[i] <- image_bc_ne_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_bc_ne_2018_df$Row[i] <- image_bc_ne_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_bc_ne_2018_df$Path[i] <- image_bc_ne_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_bc_ne_2019$features))
{
  image_bc_ne_2019_df$Date[i] <- image_bc_ne_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_bc_ne_2019_df$Row[i] <- image_bc_ne_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_bc_ne_2019_df$Path[i] <- image_bc_ne_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_bc_ne_2020$features))
{
  image_bc_ne_2020_df$Date[i] <- image_bc_ne_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_bc_ne_2020_df$Row[i] <- image_bc_ne_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_bc_ne_2020_df$Path[i] <- image_bc_ne_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_bc_ne_2018_df <- extraction_date(image_bc_ne_2018_df)
image_bc_ne_2019_df <- extraction_date(image_bc_ne_2019_df)
image_bc_ne_2020_df <- extraction_date(image_bc_ne_2020_df)

image_bc_ne_2018_df <- image_bc_ne_2018_df[,c(-1:-2)]
image_bc_ne_2019_df <- image_bc_ne_2019_df[,c(-1:-2)]
image_bc_ne_2020_df <- image_bc_ne_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_bc_ne <- do.call('rbind', list(image_bc_ne_2018_df,image_bc_ne_2019_df,image_bc_ne_2020_df))
Image_journee_chaude_bc_ne <- Image_dispo_bc_ne[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "BRITISH COLUMBIA"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_bc_ne))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_bc_ne$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_bc_ne <- rbind(Image_journee_chaude_bc_ne, Image_dispo_bc_ne[i,])
    }
  }
  print(i)
}

Image_journee_chaude_bc_ne <- Image_journee_chaude_bc_ne[-1,]

#in csv format
write.csv(Image_journee_chaude_bc_ne, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#New Brunswick
```{r eval=FALSE}
region_NB <- ee$Geometry$BBox(-69.07, 44.65, -63.66, 48.17) #Coordinates of a polygon covering New Brunswick
image_NB_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_NB)
image_NB_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_NB)
image_NB_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_NB)

image_NB_2018 <- image_NB_2018$getInfo()
image_NB_2018_df <- data.frame(1, c(1:length(image_NB_2018$features)))
image_NB_2018_df$Date <- 1
image_NB_2018_df$Row <- 1
image_NB_2018_df$Path <- 1

image_NB_2019 <- image_NB_2019$getInfo()
image_NB_2019_df <- data.frame(1, c(1:length(image_NB_2019$features)))
image_NB_2019_df$Date <- 1
image_NB_2019_df$Row <- 1
image_NB_2019_df$Path <- 1

image_NB_2020 <- image_NB_2020$getInfo()
image_NB_2020_df <- data.frame(1, c(1:length(image_NB_2020$features)))
image_NB_2020_df$Date <- 1
image_NB_2020_df$Row <- 1
image_NB_2020_df$Path <- 1

for (i in 1:length(image_NB_2018$features))
{
  image_NB_2018_df$Date[i] <- image_NB_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_NB_2018_df$Row[i] <- image_NB_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_NB_2018_df$Path[i] <- image_NB_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_NB_2019$features))
{
  image_NB_2019_df$Date[i] <- image_NB_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_NB_2019_df$Row[i] <- image_NB_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_NB_2019_df$Path[i] <- image_NB_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_NB_2020$features))
{
  image_NB_2020_df$Date[i] <- image_NB_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_NB_2020_df$Row[i] <- image_NB_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_NB_2020_df$Path[i] <- image_NB_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_NB_2018_df <- extraction_date(image_NB_2018_df)
image_NB_2019_df <- extraction_date(image_NB_2019_df)
image_NB_2020_df <- extraction_date(image_NB_2020_df)

image_NB_2018_df <- image_NB_2018_df[,c(-1:-2)]
image_NB_2019_df <- image_NB_2019_df[,c(-1:-2)]
image_NB_2020_df <- image_NB_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_NB <- do.call('rbind', list(image_NB_2018_df,image_NB_2019_df,image_NB_2020_df))
Image_journee_chaude_NB <- Image_dispo_NB[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "NEW BRUNSWICK"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_NB))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_NB$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_NB <- rbind(Image_journee_chaude_NB, Image_dispo_NB[i,])
    }
  }
  print(i)
}

Image_journee_chaude_NB <- Image_journee_chaude_NB[-1,]

#in csv format
write.csv(Image_journee_chaude_NB, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Nova Scotia
```{r eval=FALSE}
region_NS <- ee$Geometry$BBox(-66.66, 43.69, -58.89, 46.48) #Coordinates of a polygon over Nova Scotia
image_NS_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_NS)
image_NS_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_NS)
image_NS_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_NS)

image_NS_2018 <- image_NS_2018$getInfo()
image_NS_2018_df <- data.frame(1, c(1:length(image_NS_2018$features)))
image_NS_2018_df$Date <- 1
image_NS_2018_df$Row <- 1
image_NS_2018_df$Path <- 1

image_NS_2019 <- image_NS_2019$getInfo()
image_NS_2019_df <- data.frame(1, c(1:length(image_NS_2019$features)))
image_NS_2019_df$Date <- 1
image_NS_2019_df$Row <- 1
image_NS_2019_df$Path <- 1

image_NS_2020 <- image_NS_2020$getInfo()
image_NS_2020_df <- data.frame(1, c(1:length(image_NS_2020$features)))
image_NS_2020_df$Date <- 1
image_NS_2020_df$Row <- 1
image_NS_2020_df$Path <- 1

for (i in 1:length(image_NS_2018$features))
{
  image_NS_2018_df$Date[i] <- image_NS_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_NS_2018_df$Row[i] <- image_NS_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_NS_2018_df$Path[i] <- image_NS_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_NS_2019$features))
{
  image_NS_2019_df$Date[i] <- image_NS_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_NS_2019_df$Row[i] <- image_NS_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_NS_2019_df$Path[i] <- image_NS_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_NS_2020$features))
{
  image_NS_2020_df$Date[i] <- image_NS_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_NS_2020_df$Row[i] <- image_NS_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_NS_2020_df$Path[i] <- image_NS_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_NS_2018_df <- extraction_date(image_NS_2018_df)
image_NS_2019_df <- extraction_date(image_NS_2019_df)
image_NS_2020_df <- extraction_date(image_NS_2020_df)

image_NS_2018_df <- image_NS_2018_df[,c(-1:-2)]
image_NS_2019_df <- image_NS_2019_df[,c(-1:-2)]
image_NS_2020_df <- image_NS_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_NS <- do.call('rbind', list(image_NS_2018_df,image_NS_2019_df,image_NS_2020_df))
Image_journee_chaude_NS <- Image_dispo_NS[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "NOVA SCOTIA"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_NS))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_NS$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_NS <- rbind(Image_journee_chaude_NS, Image_dispo_NS[i,])
    }
  }
  print(i)
}

Image_journee_chaude_NS <- Image_journee_chaude_NS[-1,]

#in csv format
write.csv(Image_journee_chaude_NS, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Prince Edward Island
```{r eval=FALSE} 
region_PEI <- ee$Geometry$BBox(-64.94, 45.44, -61.15, 47.04) #Coordinates of a polygon over Prince Edward Island
image_PEI_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_PEI)
image_PEI_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_PEI)
image_PEI_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_PEI)

image_PEI_2018 <- image_PEI_2018$getInfo()
image_PEI_2018_df <- data.frame(1, c(1:length(image_PEI_2018$features)))
image_PEI_2018_df$Date <- 1
image_PEI_2018_df$Row <- 1
image_PEI_2018_df$Path <- 1

image_PEI_2019 <- image_PEI_2019$getInfo()
image_PEI_2019_df <- data.frame(1, c(1:length(image_PEI_2019$features)))
image_PEI_2019_df$Date <- 1
image_PEI_2019_df$Row <- 1
image_PEI_2019_df$Path <- 1

image_PEI_2020 <- image_PEI_2020$getInfo()
image_PEI_2020_df <- data.frame(1, c(1:length(image_PEI_2020$features)))
image_PEI_2020_df$Date <- 1
image_PEI_2020_df$Row <- 1
image_PEI_2020_df$Path <- 1

for (i in 1:length(image_PEI_2018$features))
{
  image_PEI_2018_df$Date[i] <- image_PEI_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_PEI_2018_df$Row[i] <- image_PEI_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_PEI_2018_df$Path[i] <- image_PEI_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_PEI_2019$features))
{
  image_PEI_2019_df$Date[i] <- image_PEI_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_PEI_2019_df$Row[i] <- image_PEI_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_PEI_2019_df$Path[i] <- image_PEI_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_PEI_2020$features))
{
  image_PEI_2020_df$Date[i] <- image_PEI_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_PEI_2020_df$Row[i] <- image_PEI_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_PEI_2020_df$Path[i] <- image_PEI_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_PEI_2018_df <- extraction_date(image_PEI_2018_df)
image_PEI_2019_df <- extraction_date(image_PEI_2019_df)
image_PEI_2020_df <- extraction_date(image_PEI_2020_df)

image_PEI_2018_df <- image_PEI_2018_df[,c(-1:-2)]
image_PEI_2019_df <- image_PEI_2019_df[,c(-1:-2)]
image_PEI_2020_df <- image_PEI_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_PEI <- do.call('rbind', list(image_PEI_2018_df,image_PEI_2019_df,image_PEI_2020_df))
Image_journee_chaude_PEI <- Image_dispo_PEI[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "PRINCE EDWARD ISLAND"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_PEI))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_PEI$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_PEI <- rbind(Image_journee_chaude_PEI, Image_dispo_PEI[i,])
    }
  }
  print(i)
}

Image_journee_chaude_PEI <- Image_journee_chaude_PEI[-1,]

#in csv format
write.csv(Image_journee_chaude_PEI, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#British Columbia east
```{r eval=FALSE}
### BC_est
region_BC_est <- ee$Geometry$BBox(-131.31, 53.24, -127.20, 55.19) #Coordinates of a polygon covering eastern British Columbia
image_BC_est_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_BC_est)
image_BC_est_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_BC_est)
image_BC_est_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_BC_est)

image_BC_est_2018 <- image_BC_est_2018$getInfo()
image_BC_est_2018_df <- data.frame(1, c(1:length(image_BC_est_2018$features)))
image_BC_est_2018_df$Date <- 1
image_BC_est_2018_df$Row <- 1
image_BC_est_2018_df$Path <- 1

image_BC_est_2019 <- image_BC_est_2019$getInfo()
image_BC_est_2019_df <- data.frame(1, c(1:length(image_BC_est_2019$features)))
image_BC_est_2019_df$Date <- 1
image_BC_est_2019_df$Row <- 1
image_BC_est_2019_df$Path <- 1

image_BC_est_2020 <- image_BC_est_2020$getInfo()
image_BC_est_2020_df <- data.frame(1, c(1:length(image_BC_est_2020$features)))
image_BC_est_2020_df$Date <- 1
image_BC_est_2020_df$Row <- 1
image_BC_est_2020_df$Path <- 1

for (i in 1:length(image_BC_est_2018$features))
{
  image_BC_est_2018_df$Date[i] <- image_BC_est_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_BC_est_2018_df$Row[i] <- image_BC_est_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_BC_est_2018_df$Path[i] <- image_BC_est_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_BC_est_2019$features))
{
  image_BC_est_2019_df$Date[i] <- image_BC_est_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_BC_est_2019_df$Row[i] <- image_BC_est_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_BC_est_2019_df$Path[i] <- image_BC_est_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
} 

for (i in 1:length(image_BC_est_2020$features))
{
  image_BC_est_2020_df$Date[i] <- image_BC_est_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_BC_est_2020_df$Row[i] <- image_BC_est_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_BC_est_2020_df$Path[i] <- image_BC_est_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_BC_est_2018_df <- extraction_date(image_BC_est_2018_df)
image_BC_est_2019_df <- extraction_date(image_BC_est_2019_df)
image_BC_est_2020_df <- extraction_date(image_BC_est_2020_df)

image_BC_est_2018_df <- image_BC_est_2018_df[,c(-1:-2)]
image_BC_est_2019_df <- image_BC_est_2019_df[,c(-1:-2)]
image_BC_est_2020_df <- image_BC_est_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_BC_est <- do.call('rbind', list(image_BC_est_2018_df,image_BC_est_2019_df,image_BC_est_2020_df))
Image_journee_chaude_BC_est <- Image_dispo_BC_est[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "BRITISH COLUMBIA"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_BC_est))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_BC_est$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_BC_est <- rbind(Image_journee_chaude_BC_est, Image_dispo_BC_est[i,])
    }
  }
  print(i)
}

Image_journee_chaude_BC_est <- Image_journee_chaude_BC_est[-1,]

#in csv format
write.csv(Image_journee_chaude_BC_est, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Yukon
```{r eval=FALSE}
region_TNO_ouest <- ee$Geometry$BBox(-135.76, 59.31, -133.92, 61.72) #Coordinates of a polygon covering the Yukon
image_TNO_ouest_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_TNO_ouest)
image_TNO_ouest_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_TNO_ouest)
image_TNO_ouest_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_TNO_ouest)

image_TNO_ouest_2018 <- image_TNO_ouest_2018$getInfo()
image_TNO_ouest_2018_df <- data.frame(1, c(1:length(image_TNO_ouest_2018$features)))
image_TNO_ouest_2018_df$Date <- 1
image_TNO_ouest_2018_df$Row <- 1
image_TNO_ouest_2018_df$Path <- 1

image_TNO_ouest_2019 <- image_TNO_ouest_2019$getInfo()
image_TNO_ouest_2019_df <- data.frame(1, c(1:length(image_TNO_ouest_2019$features)))
image_TNO_ouest_2019_df$Date <- 1
image_TNO_ouest_2019_df$Row <- 1
image_TNO_ouest_2019_df$Path <- 1

image_TNO_ouest_2020 <- image_TNO_ouest_2020$getInfo()
image_TNO_ouest_2020_df <- data.frame(1, c(1:length(image_TNO_ouest_2020$features)))
image_TNO_ouest_2020_df$Date <- 1
image_TNO_ouest_2020_df$Row <- 1
image_TNO_ouest_2020_df$Path <- 1

for (i in 1:length(image_TNO_ouest_2018$features))
{
  image_TNO_ouest_2018_df$Date[i] <- image_TNO_ouest_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_TNO_ouest_2018_df$Row[i] <- image_TNO_ouest_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_TNO_ouest_2018_df$Path[i] <- image_TNO_ouest_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_TNO_ouest_2019$features))
{
  image_TNO_ouest_2019_df$Date[i] <- image_TNO_ouest_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_TNO_ouest_2019_df$Row[i] <- image_TNO_ouest_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_TNO_ouest_2019_df$Path[i] <- image_TNO_ouest_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_TNO_ouest_2020$features))
{ 
  image_TNO_ouest_2020_df$Date[i] <- image_TNO_ouest_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Date
  image_TNO_ouest_2020_df$Row[i] <- image_TNO_ouest_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_TNO_ouest_2020_df$Path[i] <- image_TNO_ouest_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_TNO_ouest_2018_df <- extraction_date(image_TNO_ouest_2018_df)
image_TNO_ouest_2019_df <- extraction_date(image_TNO_ouest_2019_df)
image_TNO_ouest_2020_df <- extraction_date(image_TNO_ouest_2020_df)

image_TNO_ouest_2018_df <- image_TNO_ouest_2018_df[,c(-1:-2)]
image_TNO_ouest_2019_df <- image_TNO_ouest_2019_df[,c(-1:-2)]
image_TNO_ouest_2020_df <- image_TNO_ouest_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_TNO_ouest <- do.call('rbind', list(image_TNO_ouest_2018_df,image_TNO_ouest_2019_df,image_TNO_ouest_2020_df))
Image_journee_chaude_TNO_ouest <- Image_dispo_TNO_ouest[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "YUKON TERRITORY"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_TNO_ouest))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_TNO_ouest$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_TNO_ouest <- rbind(Image_journee_chaude_TNO_ouest, Image_dispo_TNO_ouest[i,])
    }
  }
  print(i)
}

Image_journee_chaude_TNO_ouest <- Image_journee_chaude_TNO_ouest[-1,]

#in csv format
write.csv(Image_journee_chaude_TNO_ouest, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```

#Northwest Territories
```{r eval=FALSE}
region_TNO_est <- ee$Geometry$BBox(-114.67, 62.29, -114.06, 62.57) #Coordinates of a polygon covering the Northwest Territory
image_TNO_est_2018 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2018-05-01', '2018-08-31')$filterBounds(region_TNO_est)
image_TNO_est_2019 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2019-05-01', '2019-08-31')$filterBounds(region_TNO_est)
image_TNO_est_2020 <- ee$ImageCollection("LANDSAT/LC08/C02/T1")$filterDate('2020-05-01', '2020-08-31')$filterBounds(region_TNO_est)

image_TNO_est_2018 <- image_TNO_est_2018$getInfo()
image_TNO_est_2018_df <- data.frame(1, c(1:length(image_TNO_est_2018$features)))
image_TNO_est_2018_df$Date <- 1
image_TNO_est_2018_df$Row <- 1
image_TNO_est_2018_df$Path <- 1

image_TNO_est_2019 <- image_TNO_est_2019$getInfo()
image_TNO_est_2019_df <- data.frame(1, c(1:length(image_TNO_est_2019$features)))
image_TNO_est_2019_df$Date <- 1
image_TNO_est_2019_df$Row <- 1
image_TNO_est_2019_df$Path <- 1

image_TNO_est_2020 <- image_TNO_est_2020$getInfo()
image_TNO_est_2020_df <- data.frame(1, c(1:length(image_TNO_est_2020$features)))
image_TNO_est_2020_df$Date <- 1
image_TNO_est_2020_df$Row <- 1
image_TNO_est_2020_df$Path <- 1

for (i in 1:length(image_TNO_est_2018$features))
{
  image_TNO_est_2018_df$Date[i] <- image_TNO_est_2018$features[i][[1]]$properties$DATE_ACQUIRED #Export Path
  image_TNO_est_2018_df$Row[i] <- image_TNO_est_2018$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_TNO_est_2018_df$Path[i] <- image_TNO_est_2018$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_TNO_est_2019$features))
{
  image_TNO_est_2019_df$Date[i] <- image_TNO_est_2019$features[i][[1]]$properties$DATE_ACQUIRED #Export Path
  image_TNO_est_2019_df$Row[i] <- image_TNO_est_2019$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_TNO_est_2019_df$Path[i] <- image_TNO_est_2019$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

for (i in 1:length(image_TNO_est_2020$features))
{
  image_TNO_est_2020_df$Date[i] <- image_TNO_est_2020$features[i][[1]]$properties$DATE_ACQUIRED #Export Path
  image_TNO_est_2020_df$Row[i] <- image_TNO_est_2020$features[i][[1]]$properties$TARGET_WRS_ROW #Export Row
  image_TNO_est_2020_df$Path[i] <- image_TNO_est_2020$features[i][[1]]$properties$TARGET_WRS_PATH #Export Path
}

image_TNO_est_2018_df <- extraction_date(image_TNO_est_2018_df)
image_TNO_est_2019_df <- extraction_date(image_TNO_est_2019_df)
image_TNO_est_2020_df <- extraction_date(image_TNO_est_2020_df)

image_TNO_est_2018_df <- image_TNO_est_2018_df[,c(-1:-2)]
image_TNO_est_2019_df <- image_TNO_est_2019_df[,c(-1:-2)]
image_TNO_est_2020_df <- image_TNO_est_2020_df[,c(-1:-2)]

#combines files together
Image_dispo_TNO_est <- do.call('rbind', list(image_TNO_est_2018_df,image_TNO_est_2019_df,image_TNO_est_2020_df))
Image_journee_chaude_TNO_est <- Image_dispo_TNO_est[1,]

#will look for the file that is the hot days, that is 30 celsius or more as maximum t in the day
donnee_meteo <- read.csv2("HOT_DAY_FILE", sep=",")
donnee_station <- read.csv2("FILE_PATH\\Station Inventory EN_2.csv", sep = ",")
donnee_meteo_2 <- merge(donnee_meteo, donnee_station, by.x = "ID.climatologique", by.y = "Climate.ID")
Ont <- donnee_meteo_2[which(donnee_meteo_2$Province == "NORTHWEST TERRITORIES"),]

#In the batch of images, not all of them correspond to hot days, so we don't download them for nothing
for (i in 1:nrow(Image_dispo_TNO_est))
{
  for (j in 1:nrow(Ont))
  {
    if(as.character(Image_dispo_TNO_est$Date[i]) == Ont$Date.Heure[j])
    {
      Image_journee_chaude_TNO_est <- rbind(Image_journee_chaude_TNO_est, Image_dispo_TNO_est[i,])
    }
  }
  print(i)
}

Image_journee_chaude_TNO_est <- Image_journee_chaude_TNO_est[-1,]

#in csv format
write.csv(Image_journee_chaude_TNO_est, "CHEMIN_DU_FICHIER_CONTENANT_LES_INFORMATIONS_NÉCESSAIRES_AU_TÉLÉCHARGEMENT")
```